\documentclass[margin]{res}
\setlength{\textwidth}{5.1in} 

\begin{document}

 \moveleft.5\hoffset\centerline{\large\bf Ramel Tranquille}
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
 \moveleft.5\hoffset\centerline{422 Newport Street, Brooklyn, New York 11207}
 \moveleft.5\hoffset\centerline{tranquilleramel@gmail.com}
 \moveleft.5\hoffset\centerline{347-496-9076}


\begin{resume}
 

\section{EDUCATION} {\sl Bachelor of Science,} Business\\
                New York University: Leonard N Stern Schoool of Business
				(2018-2022)\\
                Concentration: Data Science\\
                Minor: Computer Science
 
 
\section{COMPUTER \\ SKILLS} {\sl Languages \& Software:} Python, Java,  
                C++, C \\
                {\sl Operating Systems:} Linux Debian/CentOS, Windows, MacOS \\ 
                {\sl Others:} Microsoft Applications, Adobe Software
 
\section{EXPERIENCE} {\sl Interlude Cafe} \hfill 2019\\
                  Barista \\ New York City, New York
                  \begin{itemize}  \itemsep -2pt
                  		\item Developed a new stocking system which
						  improved the overall efficiency of the 
						  cafe overall
						\item Learned the ins and out of high quality coffee, matcha, and teas
                 \end{itemize}
 
\section{COMMUNITY \\ SERVICE}  {\sl The Door Service Projects} \hfill 2016-2019 \\
				Volunteer and Community Maintenance \\ New York City, New York
				\begin{itemize} \itemsep -2pt
						\item Worked with Meals on Wheels to deliver food to 
								handicapped and elderly people throughout
								NYC. Took initiative to devise creative routes 
								to increase efficiency of deliveries.
						\item Worked to maintain different communities such as SoHo, 
								multiple Bronx parks, and Governor’s
								Island. Helped to motivate coworkers through difficult 
								challenges while working.
						\item Volunteered at the NYC Rescue Mission to help feed and 
								shelter homeless people throughout
								NYC. Also stayed for a longer period of time to 
								assist with food preparation. 
						\item Coordinated the development of a lemonade stand and 
								donated all proceeds to cancer
								research. Came up with the initial idea to 
								create lemonade stand and found a creative way to
								maneuver the stand around parks, increasing the number of sales.
				\end{itemize}

				
\section{EXTRA-CURRICULAR \\ ACTIVITIES}  
			\begin{itemize}
						\item HighSchool Coding League Founder 
						\item HighSchool Volleyball Founder and Captain 
						\item HighSchool Basketball Captain
						\item HighSchool Flag Football Captain
			\end{itemize}

\end{resume}
\end{document}




